Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-24 manuscript/ERL_global_C_review.Rmd
small update

---
title: ""
output: 
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: environmental-research-letters.csl

@@

Of the `r nrow(ForC_measurements)` in ForC v.#, `r n_records` met the criteria for inclusion in this study (Fig. 1). 
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained mature forest estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_matureTrB_with_ge7_areas` fluxes and `r n_stocks_matureTrB_with_ge7_areas` stocks in tropical broadleaf forests, `r n_fluxes_matureTeB_with_ge7_areas` fluxes and `r n_stocks_matureTeB_with_ge7_areas` stocks in temperate broadleaf forests, `r n_fluxes_matureTeN_with_ge7_areas` fluxes and `r n_stocks_matureTeN_with_ge7_areas` stocks in temperate conifer forests, and `r n_fluxes_matureBoN_with_ge7_areas` fluxes and `r n_stocks_matureBoN_with_ge7_areas` stocks in boreal forests. 
For regrowth forests (<100 yrs), ForC contained estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_youngTrB_with_ge7_areas` fluxes and `r n_stocks_youngTrB_with_ge7_areas` stocks in tropical broadleaf forests, `r n_fluxes_youngTeB_with_ge7_areas` fluxes and `r n_stocks_youngTeB_with_ge7_areas` stocks in temperate broadleaf forests, `r n_fluxes_youngTeN_with_ge7_areas` fluxes and `r n_stocks_youngTeN_with_ge7_areas` stocks in temperate conifer forests, and `r n_fluxes_youngBoN_with_ge7_areas` fluxes and `r n_stocks_youngBoN_with_ge7_areas` stocks in boreal forests.

>>>>

---
title: ""
output: 
  word_document:
    fig_caption: yes
bibliography: references.bib
csl: environmental-research-letters.csl

@@

Of the `r nrow(ForC_measurements)` records in ForC v.#, `r n_records` met the criteria for inclusion in this study (Fig. 1). 
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained mature forest estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_matureTrB_with_ge7_areas` fluxes and `r n_stocks_matureTrB_with_ge7_areas` stocks in tropical broadleaf forests, `r n_fluxes_matureTeB_with_ge7_areas` fluxes and `r n_stocks_matureTeB_with_ge7_areas` stocks in temperate broadleaf forests, `r n_fluxes_matureTeN_with_ge7_areas` fluxes and `r n_stocks_matureTeN_with_ge7_areas` stocks in temperate conifer forests, and `r n_fluxes_matureBoN_with_ge7_areas` fluxes and `r n_stocks_matureBoN_with_ge7_areas` stocks in boreal forests. 
For regrowth forests (<100 yrs), ForC contained estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_youngTrB_with_ge7_areas` fluxes and `r n_stocks_youngTrB_with_ge7_areas` stocks in tropical broadleaf forests, `r n_fluxes_youngTeB_with_ge7_areas` fluxes and `r n_stocks_youngTeB_with_ge7_areas` stocks in temperate broadleaf forests, `r n_fluxes_youngTeN_with_ge7_areas` fluxes and `r n_stocks_youngTeN_with_ge7_areas` stocks in temperate conifer forests, and `r n_fluxes_youngBoN_with_ge7_areas` fluxes and `r n_stocks_youngBoN_with_ge7_areas` stocks in boreal forests.
